Using Deep Learning to Identify Cognitive Impairment in Electronic Health Records

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
mostly done with results section

We evaulated each model based on sequence level class assignments. Model performance for each model in shown in \tableref{tab:table2}. TF-IDF achieved AUC of 0.95 and accuracy f 0.84. The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix B. While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match, which occasionally would negate the presence of CI. This led to the model over-zealously predicting sequences as demonstrating CI. ClincalBERT was able to overcome these issues due to its high complexity transformer architecture, and achieved AUC of 0.98 and accuracy of 0.93.

@@

% Appendix C
\section{Top TF-IDF Word Features}
\begin{table}[hbtp]
    {\begin{tabular}{cccc}
    \toprule 
    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr &
    \midrule

>>>>

We evaulated each model based on sequence level class assignments. Model performance for each model in shown in \tableref{tab:table2}. TF-IDF achieved AUC of 0.95 and accuracy f 0.84. The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix \ref{app:app3}. While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match, which occasionally would negate the presence of CI. This led to the model over-zealously predicting sequences as demonstrating CI. ClinicalBERT was able to overcome these issues due to its high complexity transformer architecture, and achieved AUC of 0.98 and accuracy of 0.93. In order to generate accurate patient level class assignments, we applied ClinicalBERT to 186,730 sequences from the N = 13,941 unique patients that were not patient of our training/validation/set sets. With these sequence level predictions, we generated patient level class assignments by empirically tuning a sequence threshold that represented the number of sequences predicted as Positive by ClinicalBERT. We identified the most optimal threshold by comparing the percentage of patients being predicted as having CI (stratified by APOE allele) to the percentages of patients with CI related Meds/ICD codes (also stratified by APOE allele). \tableref{tab:table4} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.

@@

% Appendix C
\section{Top TF-IDF Word Features} \label{app:app3}
\begin{table}[hbtp]
    {\begin{tabular}{cccc}
    \toprule 
    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr &
    \midrule
